Untitled

### 2014-11-29 GEMDataSource.Rmd
Merged GEMAnnual data

# Library required packages repmis, ridy, reshape2, plyr and WDI packages
library(plyr)
library(repmis)
library(tidyr)
library(reshape2)
library(WDI)
library(foreign)

# Load citation package
pkgs <- c('plyr','repmis', 'tidyr', 'reshape2', 'WDI', 'stargazer', 'Zelig')
repmis::LoadandCite(pkgs, file= 'DataRpackageCitations.bib')

@@

# Import 2010GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is

SupportiveTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEMAvgIndicators.csv", header = TRUE, cache = FALSE)

@@

### Clean SupportiveTeaching

### Create new data frame without unnecessary data
WayOfTeaching <- SupportiveTeaching[, c("NES10CRNAME", "NES10_D01_MEAN")]

## as.factor("WayOfTeaching")

##TWayofTeaching <- SupportiveTeaching[c("Australia", "Austria", "Belgium", "Canada", "Chile", "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Japan", "Korea", "Luxemburg", "Mexico", "Netherlands", "New Zealand", "Norway", "Poland", "Portugal", "Slovak Republic", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom", "United States"),])

@@

# Edit column names for each dataframe
names(Clean01) <- gsub("ki01d01", "2001", names(Clean01))
names(Clean01) <- gsub("country", "Country", names(Clean01))
names(Clean02) <- gsub("ki02d01", "2002", names(Clean02))
names(Clean02) <- gsub("country", "Country", names(Clean02))
names(Clean03) <- gsub("ki03d01", "2003", names(Clean03))
names(Clean03) <- gsub("country", "Country", names(Clean03))
names(Clean04) <- gsub("ki04d01", "2004", names(Clean04))
names(Clean04) <- gsub("ki04ctry", "Country", names(Clean04))
names(Clean05) <- gsub("KI05D01", "2005", names(Clean05))
names(Clean05) <- gsub("KI05ctry", "Country", names(Clean05))
names(Clean06) <- gsub("KI06D01_mean", "2006", names(Clean06))
names(Clean06) <- gsub("KI06CTRY", "Country", names(Clean06))
names(Clean07) <- gsub("ki07d01_", "2007", names(Clean07))
names(Clean07) <- gsub("ki07ctry", "Country", names(Clean07))
names(Clean08) <- gsub("NES08_D01_MEAN", "2008", names(Clean08))
names(Clean08) <- gsub("NES08COUNTRY", "Country", names(Clean08))
names(Clean09) <- gsub("NES09_D01_MEAN", "2009", names(Clean09))
names(Clean09) <- gsub("NES09COUNTRY", "Country", names(Clean09))
names(Clean10) <- gsub("NES10_D01_MEAN", "2010", names(Clean10))
names(Clean10) <- gsub("NES10CRNAME", "Country", names(Clean10))

@@

#### Import WDI Annual GDP Growth Data ####
GDPGrowth = WDI(indicator='NY.GDP.MKTP.KD.ZG', country=c('MX','CA','US','FR','AU','AT','BE',
                                                         'CL','CZ','DK','EE','FI','DE','HU', 
                                                         'IS','IE','IL','IT','JP','KR','LU',
                                                         'NL','NZ','NO','PL','PT','SK','SI',
                                                         'ES','SE','CH','TR','GB','US','GR'), 
                start=2001, end=2013)
# Rename columns
GDPGrowth <- plyr::rename(x = GDPGrowth, 
                                      replace = c("year" = "Year",
                                                  "NY.GDP.MKTP.KD.ZG" = "AnnualGDPGrowth",
                                                  "country" = "Country"))

# Recode country == "United States" to "United States of America" and Korea, Rep. to Korea (South)
GDPGrowth$Country[GDPGrowth$Country == "United States"] <- "United States of America"

# Recode country == "Korea, Rep."" to "Korea (South)"
GDPGrowth$Country[GDPGrowth$Country == "Korea, Rep."] <- "Korea (South)"

# Remove iso2c data to ease merge with FinalMerge data
GDPGrowth$iso2c <- NULL

# Merge GDPGrowth and FinalGEM
CompleteDataset <- merge(FinalGEM, GDPGrowth,
                   union("Country", "Year"),
                   all = TRUE)

@@

# Merge GEMNES country level data
Merged1 <- merge(Clean01, Clean02, all = TRUE)
Merged2 <- merge(Clean03, Clean04, all = TRUE)
Merged3 <- merge(Clean05, Clean06, all = TRUE)
Merged4 <- merge(Clean07, Clean08, all = TRUE)
Merged5 <- merge(Clean09, Clean10, all = TRUE)
Merged6 <- merge(Merged1, Merged2, all = TRUE)
Merged7 <- merge(Merged3, Merged4, all = TRUE)
Merged8 <- merge(Merged5, Merged6, all = TRUE)
Merged9 <- merge(Merged7, Merged8, all = TRUE)

# Recode countries
Merged9$Country[Merged9$Country == "AUSTRALIA"] <- "Australia"
Merged9$Country[Merged9$Country == "AUSTRIA"] <- "Austria"
Merged9$Country[Merged9$Country == "BELGIUM"] <- "Belgium"
Merged9$Country[Merged9$Country == "CANADA"] <- "Canada"
Merged9$Country[Merged9$Country == "CHILE"] <- "Chile"
Merged9$Country[Merged9$Country == "CZECH REPUBLIC"] <- "Czech Republic"
Merged9$Country[Merged9$Country == "DENMARK"] <- "Denmark"
Merged9$Country[Merged9$Country == "ESTONIA"] <- "Estonia"
Merged9$Country[Merged9$Country == "FINLAND"] <- "Finland"
Merged9$Country[Merged9$Country == "FRANCE"] <- "France"
Merged9$Country[Merged9$Country == "GERMANY"] <- "Germany"
Merged9$Country[Merged9$Country == "GREECE"] <- "Greece"
Merged9$Country[Merged9$Country == "HUNGARY"] <- "Hungary"
Merged9$Country[Merged9$Country == "ICELAND"] <- "Iceland"
Merged9$Country[Merged9$Country == "IRELAND"] <- "Ireland"
Merged9$Country[Merged9$Country == "ISRAEL"] <- "Israel"
Merged9$Country[Merged9$Country == "ITALY"] <- "Italy"
Merged9$Country[Merged9$Country == "JAPAN"] <- "Japan"
Merged9$Country[Merged9$Country == "KOREA"] <- "South Korea"
Merged9$Country[Merged9$Country == "LUXEMBURG"] <- "Luxemburg"
Merged9$Country[Merged9$Country == "MEXICO"] <- "Mexico"
Merged9$Country[Merged9$Country == "NETHERLANDS"] <- "Netherlands"
Merged9$Country[Merged9$Country == "NEW ZEALAND"] <- "New Zealand"
Merged9$Country[Merged9$Country == "NORWAY"] <- "Norway"
Merged9$Country[Merged9$Country == "POLAND"] <- "Poland"
Merged9$Country[Merged9$Country == "PORTUGAL"] <- "Portugal"
Merged9$Country[Merged9$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
Merged9$Country[Merged9$Country == "SLOVENIA"] <- "SLOVENIA"
Merged9$Country[Merged9$Country == "SPAIN"] <- "Spain"
Merged9$Country[Merged9$Country == "SWEDEN"] <- "Sweden"
Merged9$Country[Merged9$Country == "SWITZERLAND"] <- "Switzerland"
Merged9$Country[Merged9$Country == "TURKEY"] <- "Turkey"
Merged9$Country[Merged9$Country == "UNITED KINGDOM"] <- "United Kingdom"
Merged9$Country[Merged9$Country == "UK"] <- "United Kingdom"
Merged9$Country[Merged9$Country == "USA"] <- "United States"
Merged9$Country[Merged9$Country == "UNITED STATES"] <- "United States"
Merged9$Country[Merged9$Country == "Korea"] <- "South Korea"

@@

# Delete unnecessary column
subset_data$row.name <- NULL

@@

@@

FinalData <- merge(CompleteDataset, subset_data,
                   union("Country", "Year"),
                   all = TRUE)

>>>>

# Library required packages repmis, ridy, reshape2, and plyr packages
library(plyr)
library(repmis)
library(tidyr)
library(reshape2)
library(foreign)

# Load citation package
pkgs <- c('plyr','repmis', 'tidyr', 'reshape2', 'stargazer', 'Zelig')
repmis::LoadandCite(pkgs, file= 'DataRpackageCitations.bib')

@@

# Import 2010GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is
SupportiveTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEMAvgIndicators.csv", header = TRUE, cache = FALSE)

@@

@@

# Edit column names for each dataframe

Clean01 <- plyr::rename(x = Clean01, 
                                      replace = c("ki01d01" = "Year01",
                                                  "country" = "Country"))

Clean02 <- plyr::rename(x = Clean02, 
                                      replace = c("ki02d01" = "Year02",
                                                  "country" = "Country"))

Clean03 <- plyr::rename(x = Clean03, 
                                      replace = c("ki03d01" = "Year03",
                                                  "country" = "Country"))

Clean04 <- plyr::rename(x = Clean04, 
                                      replace = c("ki04d01" = "Year04",
                                                  "ki04ctry" = "Country"))

Clean05 <- plyr::rename(x = Clean05, 
                                      replace = c("KI05D01" = "Year05",
                                                  "KI05ctry" = "Country"))

Clean06 <- plyr::rename(x = Clean06, 
                                      replace = c("KI06D01_mean" = "Year06",
                                                  "KI06CTRY" = "Country"))
Clean07 <- plyr::rename(x = Clean07, 
                                      replace = c("ki07d01_" = "Year07",
                                                  "ki07ctry" = "Country"))

Clean08 <- plyr::rename(x = Clean08, 
                                      replace = c("NES08_D01_MEAN" = "Year08",
                                                  "NES08COUNTRY" = "Country"))

Clean09 <- plyr::rename(x = Clean09, 
                                      replace = c("NES09_D01_MEAN" = "Year09",
                                                  "NES09COUNTRY" = "Country"))

Clean10 <- plyr::rename(x = Clean10, 
                                      replace = c("NES10_D01_MEAN" = "Year10",
                                                  "NES10CRNAME" = "Country"))

@@

@@

CleanMerge <- cbind(names = c(rownames(Clean01), rownames(Clean02), rownames(Clean03),
                              rownames(Clean04), rownames(Clean05), rownames(Clean06),
                              rownames(Clean07), rownames(Clean08), rownames(Clean09),
                              rownames(Clean10)),
                    rbind.fill(list(Clean01, Clean02, Clean03, Clean04, Clean05, Clean06,
                                    Clean07, Clean08, Clean09, Clean10)))

# Recode countries
CleanMerge$Country[CleanMerge$Country == "AUSTRALIA"] <- "Australia"
CleanMerge$Country[CleanMerge$Country == "AUSTRIA"] <- "Austria"
CleanMerge$Country[CleanMerge$Country == "BELGIUM"] <- "Belgium"
CleanMerge$Country[CleanMerge$Country == "CANADA"] <- "Canada"
CleanMerge$Country[CleanMerge$Country == "CHILE"] <- "Chile"
CleanMerge$Country[CleanMerge$Country == "CZECH REPUBLIC"] <- "Czech Republic"
CleanMerge$Country[CleanMerge$Country == "DENMARK"] <- "Denmark"
CleanMerge$Country[CleanMerge$Country == "ESTONIA"] <- "Estonia"
CleanMerge$Country[CleanMerge$Country == "FINLAND"] <- "Finland"
CleanMerge$Country[CleanMerge$Country == "FRANCE"] <- "France"
CleanMerge$Country[CleanMerge$Country == "GERMANY"] <- "Germany"
CleanMerge$Country[CleanMerge$Country == "GREECE"] <- "Greece"
CleanMerge$Country[CleanMerge$Country == "HUNGARY"] <- "Hungary"
CleanMerge$Country[CleanMerge$Country == "ICELAND"] <- "Iceland"
CleanMerge$Country[CleanMerge$Country == "IRELAND"] <- "Ireland"
CleanMerge$Country[CleanMerge$Country == "ISRAEL"] <- "Israel"
CleanMerge$Country[CleanMerge$Country == "ITALY"] <- "Italy"
CleanMerge$Country[CleanMerge$Country == "JAPAN"] <- "Japan"
CleanMerge$Country[CleanMerge$Country == "KOREA"] <- "South Korea"
CleanMerge$Country[CleanMerge$Country == "LUXEMBURG"] <- "Luxemburg"
CleanMerge$Country[CleanMerge$Country == "MEXICO"] <- "Mexico"
CleanMerge$Country[CleanMerge$Country == "NETHERLANDS"] <- "Netherlands"
CleanMerge$Country[CleanMerge$Country == "NEW ZEALAND"] <- "New Zealand"
CleanMerge$Country[CleanMerge$Country == "NORWAY"] <- "Norway"
CleanMerge$Country[CleanMerge$Country == "POLAND"] <- "Poland"
CleanMerge$Country[CleanMerge$Country == "PORTUGAL"] <- "Portugal"
CleanMerge$Country[CleanMerge$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
CleanMerge$Country[CleanMerge$Country == "SLOVENIA"] <- "SLOVENIA"
CleanMerge$Country[CleanMerge$Country == "SPAIN"] <- "Spain"
CleanMerge$Country[CleanMerge$Country == "SWEDEN"] <- "Sweden"
CleanMerge$Country[CleanMerge$Country == "SWITZERLAND"] <- "Switzerland"
CleanMerge$Country[CleanMerge$Country == "TURKEY"] <- "Turkey"
CleanMerge$Country[CleanMerge$Country == "UNITED KINGDOM"] <- "United Kingdom"
CleanMerge$Country[CleanMerge$Country == "UK"] <- "United Kingdom"
CleanMerge$Country[CleanMerge$Country == "USA"] <- "United States"
CleanMerge$Country[CleanMerge$Country == "UNITED STATES"] <- "United States"
CleanMerge$Country[CleanMerge$Country == "Korea"] <- "South Korea"
CleanMerge$Country[CleanMerge$Country == "US"] <- "United States"

# Set columns to numeric
CleanMerge[,"Year01"] <- as.numeric(CleanMerge[,"Year01"])
CleanMerge[,"Year02"] <- as.numeric(CleanMerge[,"Year02"])
CleanMerge[,"Year03"] <- as.numeric(CleanMerge[,"Year03"])
CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year04"])
CleanMerge[,"Year05"] <- as.numeric(CleanMerge[,"Year05"])
CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year06"])
CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year07"])
CleanMerge[,"Year08"] <- as.numeric(CleanMerge[,"Year08"])
CleanMerge[,"Year09"] <- as.numeric(CleanMerge[,"Year09"])
CleanMerge[,"Year10"] <- as.numeric(CleanMerge[,"Year10"])

ddply(pp, .(names), function(x) colSums(x[,-1], na.rm = TRUE))

ddply(CleanMerge, .(names), function(x) colSums(x[,-1], na.rm = TRUE))

arrange()

@@

# Delete unnecessary column
subset_data$row.names <- NULL

@@

GrandData1 <- GrandData[order("Country",)]

@@

FinalData <- merge(FinalGEM, GrandData,
                   union("Country", "Year"))

### 2014-11-29 Misc/TrialFile.Rmd
Merged GEMAnnual data

>>>>

``` {r}

#### Import WDI Annual GDP Growth Data ####
GDPGrowth = WDI(indicator='NY.GDP.MKTP.KD.ZG', country=c('MX','CA','US','FR','AU','AT','BE',
                                                         'CL','CZ','DK','EE','FI','DE','HU', 
                                                         'IS','IE','IL','IT','JP','KR','LU',
                                                         'NL','NZ','NO','PL','PT','SK','SI',
                                                         'ES','SE','CH','TR','GB','US','GR'), 
                start=2001, end=2013)
# Rename columns
GDPGrowth <- plyr::rename(x = GDPGrowth, 
                                      replace = c("year" = "Year",
                                                  "NY.GDP.MKTP.KD.ZG" = "AnnualGDPGrowth",
                                                  "country" = "Country"))

# Recode country == "United States" to "United States of America" and Korea, Rep. to Korea (South)
GDPGrowth$Country[GDPGrowth$Country == "United States"] <- "United States of America"

# Recode country == "Korea, Rep."" to "Korea (South)"
GDPGrowth$Country[GDPGrowth$Country == "Korea, Rep."] <- "Korea (South)"

# Remove iso2c data to ease merge with FinalMerge data
GDPGrowth$iso2c <- NULL

# Merge GDPGrowth and FinalGEM
CompleteDataset <- merge(FinalGEM, GDPGrowth,
                   union("Country", "Year"),
                   all = TRUE)
